Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-12-24 journal-draft/ettdoc_JG.tex
minor change

To formulate the debatable nodes' membership clarification into a congestion game, we see this process from a different perspective. 
In particular, for a debatable node, instead being in all its claiming clusters, now it is not included in any claiming cluster and it needs to decide on one cluster to join.
When a debatable node $i$ joins one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
Then, node $i$ chooses the cluster $C$, where the decrease of CCs in cluster $C$ is smaller than the decrease if $i$ would have joined any other claiming cluster in $S_i$.
The relation between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.

>>>>

To formulate the debatable nodes' membership clarification into a congestion game, we see the process from a different perspective. 
In particular, for a debatable node, instead being in all its claiming clusters, we see it is not included in any claiming cluster and it needs to decide on one cluster to join.
When a debatable node $i$ joins one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
Then, node $i$ chooses the cluster $C$, where the decrease of CCs in cluster $C$ is smaller than the decrease if $i$ would have joined any other claiming cluster in $S_i$.
The relation between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
